Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2021-01-28 vesicle_code/docs/permeableVes/main.tex
worked on discussion

Using scaling arguments, we showed that permeability due to osmolarity
is two orders of magnitude larger than permeability due to tension, and
six orders of magnitude larger than permeability due to bending.
Therefore, future studies will investigate semi-permeability in the
presence of a solute concentration. The presence of such a solute
concentrations is responsible for many physiological processes including
cell migration in confined
microenvironments~\cite{StrokaJiangChenEtAl2014_Cell},
dialysis~\cite{wan2006}, and
apoptosis~\cite{marchetti1996mitochondrial}. We plan to investigate
vesicle motion in a solute in the zero Peclet number limit which was
analyzed for spherical vesicles by Anderson~\cite{and1983} and more
general shapes using a finite element method by Jaeger {\em et
al.}~\cite{jae-car-med-try1999}.

>>>>

Using scaling arguments, we showed that permeability due to osmolarity
is two orders of magnitude larger than permeability due to tension, and
six orders of magnitude larger than permeability due to bending.
Therefore, future studies will investigate semipermeable membranes
suspended in a solvent with a solute concentration. The presence of a
solute is responsible for many physiological processes including cell
migration in confined
microenvironments~\cite{StrokaJiangChenEtAl2014_Cell,
papadopoulos2008aquaporins}, dialysis~\cite{wan2006}, cell
desiccation~\cite{vogl2014effect}, and
apoptosis~\cite{marchetti1996mitochondrial}. While the solute dynamics
is governed by an advection-diffusion equation, many biophysical
applications involve speeds no greater than $\sim 50$
$\mu$m/hour~\cite{StrokaJiangChenEtAl2014_Cell}, a length scale of 10
$\mu$m, and a solute diffusivity of $\sim 10^{-10}$ m$^2$/s (glucose in
water). The resulting Peclet number is $\sim 10^{-2}$, and this limit
has been analyzed for spherical vesicles by Anderson~\cite{and1983} and
more general shapes using a finite element method by Jaeger {\em et
al.}~\cite{jae-car-med-try1999}. Since the dynamics of the concentration
is diffusion-dominated, we will use a stable and accurate boundary
integral method that is similar to the numerical method we apply to the
hydrodynamics (see Supplementary Material).
